Thesis: draft

### 2021-05-21 draft.tex
Update draft.tex
changed section 3.6

@@

% introduce dynamics of social platform under study and link to social networks from previous chapter!!

This thesis follows the opinion dynamics model that was designed by Perra and Rocha \cite{Perra2019}. We start with a network with $N = 10^3$ actors.  Initially, each actor is given one of two opinions, A or B. Each time step a random fraction equal to $p= 0.1$ of these actors becomes active, where $p$ is the constant activation probability. Every time step, all active actors update their opinion synchronously. This updating is done as follows. First, the active actor broadcasts its current opinion to all its neighbors. Then, it updates its own opinion according to the opinions on its time-line $R_i(t)$. This time-line contains only a selection of all the opinions received from its friends, which is the fundamental idea behind algorithmic personalization. Each user has a hidden time-line $L_i(t)$ which contains the time-line of the actor at the last time it was active ($R_i(t_{\text{last}})$) plus all the post that its friends posted during $\interval[right open fence =), open right]{t_\text{last}}{t}$. If an actor becomes active, the filtering algorithm select $S = 20$ items from this hidden time-line $L_i(t)$. These $20$ items then form the actual time-line $R_i(t)$ of the actor. Updating is done according to the probabilistic majority model: an actor who sees $20\%$ of the posts promoting opinion A and thus $80\%$ promoting opinion B will adopt opinion A with a chance $p_\text{A} = 0.2$ and opinion B with a chance $p_\text{B} = 0.8$. If another model is used, e.g. the majority model, this will be explicitly stated.
% Add pictorial representation of model??

@@

Perra and Rocha proposed different ways of selecting the $S$ items from the hidden time-line $L_i(t)$ \cite{Perra2019}. We will implement three of their algorithms: (i) REF filtering: $S$ random items from the hidden time-line $L_i(t)$ are selected and show on the actual time-line $R_i(t)$; (ii) REC filtering: the $S$ most recent posts in the hidden time-line $L_i(t)$ are displayed on the actual time-line $R_i(t)$ and (iii) PR filtering: this way of filtering is based on semantic filtering explained in Section \ref{filter}; the post in the hidden time-line $L_i(t)$ are ordered according to the current opinion of the actor (if the actor has opinion A, the hidden time-line will be ordered as AAAA...BBB), then the $S$ first items are selected and shown on the time-line $R_i(t)$.\\
\newline
The base-line algorithms are the REF and REC filtering algorithms. Filtering tailored to the user's preferences is accomplished with the PR filtering algorithm.

@@

If we want to introduce stubbornness in the model we will mainly use the resistance parameter, as explained in Section \ref{stubbBin}. Lets briefly summarize this concept of stubbornness. Each actor is given a resistance parameter $r_i$, with $0 \leqslant r_i \leqslant 1$; $r_i = 0$ means not stubborn and $r_i = 1$ means completely stubborn. For all intermediate values of $r_i$, a random number $f$ between zero and one is drawn; if $f > r_i$, the actor can update its opinion, if $f \leqslant r_i$, the actor will keep its current opinion.\\
\newline
Some results for the majority threshold model, also explained in Section \ref{stubbBin}, will be shared as well. This is, however, not the main stubbornness model that we will focus on. If this model is used, this will be explicitly stated. \\
\newline
Some pseudo-code is given in Algorithm \ref{alg:update} to make the model more comprehensive and understandable. The pseudo-code for updating the opinions of the active actors in case of using a resistance parameter $r$ at time step $t$ is displayed.

>>>>

We want to model opinion dynamics on social media platforms, with focus on Facebook. Each time we access Facebook we experience algorithmic personalization. The time-line or News Feed of each user on Facebook is the complex combination of posts from, among other, Facebook friends, companies and mass media. In 2013, Facebook reported that on average 1500 potential stories of friends and pages we follow or companies that are sponsored could be shown on the News Feed of each user. % add ref Facebook
No user could ever process this amount of information, hence, Facebook selects around 300 of them, which then appear on your personalized News Feed. Their selection methods are based on (i) how often we interact with certain friends, pages or prominent figures; (ii) the amount of likes, shares and comments a post receives from your friends and others; (iii) how much you have interacted with certain types of posts before and (iv) whether you and other people on Facebook are hiding or reporting a certain post. \\
\newline
If we translate Facebook to a social network, we end up with a temporal network. Nodes represent the Facebook users, which become active and inactive over time. Edges represent friendship ties on Facebook, that is, they link an user to his Facebook friends and the pages he or she follows. Each node then has an attribute that needs to mimic the Facebook News Feed and which is susceptible to the filtering algorithm.

@@

This thesis follows the opinion dynamics model that was designed by Perra and Rocha \cite{Perra2019}. We start with a network with $N = 10^3$ actors.  Initially, each actor is given one of two opinions, A or B. Each time step a random fraction equal to $p= 0.1$ of these actors becomes active, where $p$ is the constant activation probability. Then, all active actors update their opinion synchronously. This updating is done as follows. First, the active actor broadcasts its current opinion to all its neighbors. Then, it updates its own opinion according to the opinions on its time-line $R_i(t)$. This time-line contains only a selection of all the opinions received from its friends, which is the fundamental idea behind algorithmic personalization. Each actor has a hidden time-line $L_i(t)$ which contains the time-line of the actor at the last time it was active ($R_i(t_{\text{last}})$) plus all the post that its friends posted during $\interval[right open fence =), open right]{t_\text{last}}{t}$. If an actor becomes active, the filtering algorithm select $S = 20$ items from this hidden time-line $L_i(t)$ and shows them on the time-line $R_i(t)$ of the actor. Updating is done according to the probabilistic majority model: an actor who sees $20\%$ of the posts promoting opinion A and thus $80\%$ promoting opinion B will adopt opinion A with a chance $p_\text{A} = 0.2$ and opinion B with a chance $p_\text{B} = 0.8$. If another model is used, e.g. the majority model, this will be explicitly stated.
% Add pictorial representation of model??

@@

Perra and Rocha proposed different ways of selecting the $S$ items from the hidden time-line $L_i(t)$ \cite{Perra2019}. We will implement three of their algorithms: (i) REF filtering: $S$ random items from the hidden time-line $L_i(t)$ are selected and shown on the actual time-line $R_i(t)$; (ii) REC filtering: the $S$ most recent posts in the hidden time-line $L_i(t)$ are displayed on the actual time-line $R_i(t)$ and (iii) PR filtering: this way of filtering is based on semantic filtering explained in Section \ref{filter}; the posts on the hidden time-line $L_i(t)$ are ordered according to the current opinion of the actor (if the actor has opinion A, the hidden time-line will be ordered as AAAA...BBB), then the $S$ first items are selected and shown on the time-line $R_i(t)$.\\
\newline
The base-line algorithms are the REF and REC filtering algorithms. Filtering tailored to the user's preferences is accomplished with the PR filtering algorithm.

@@

If we want to introduce stubbornness in the model we will mainly use the resistance parameter, as explained in Section \ref{stubbBin}. Lets briefly summarize this concept of stubbornness. Each actor is given a resistance parameter $r_i$, with $0 \leqslant r_i \leqslant 1$; $r_i = 0$ means not stubborn and $r_i = 1$ means completely stubborn. For all intermediate values of $r_i$, a random number $f$ between zero and one is drawn; if $f > r_i$, the actor can update its opinion, if $f \leqslant r_i$, the actor will keep its current opinion.\\
\newline
Some results for the majority threshold model, also explained in Section \ref{stubbBin}, will be shared as well. This is not the main stubbornness model that we will focus on. If this model is used, this will be explicitly stated. \\
\newline
Some pseudo-code is given in Algorithm \ref{alg:update} to make the model more comprehensive and understandable. The pseudo-code for updating the opinions of the active actors in case of using a resistance parameter $r$ at time step $t$ is displayed.
